% LaTeX resume using res.cls
\documentclass[line,margin,12pt ]{res} 
\usepackage{extsizes}
\usepackage{hyperref}
\usepackage[margin=10.0in]{geometry}
\usepackage{textcomp}
\topmargin=-5in
\oddsidemargin =-15in
\setlength{\textheight}{10in}
\setlength{\leftskip}{-5mm}

\newsectionwidth{45mm}



%\usepackage{enumitem}
%\setlength{\itemindent}{1in}
%

\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0.5pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{2pt} % allow room for 2-line header
\setlength{\headsep}{12pt}  % space between header and text
\setlength{\headheight}{12pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
                                 % the foot is empty

\lhead{\bf {\it Rajesh Prashanth}{\it\hfill page. \thepage} }
% put text in header (right side)
%
                                  % the foot is empty
\geometry{%
  left=12mm,
  right=60mm,
  top=20mm,
  bottom=20mm,
  bindingoffset=0cm,
  headheight=15pt,% output from geometry tells you what this needs to be set to as a minimum
}
%
%


%


\lfoot{\it Last update: \today
}   
\cfoot{}

\fancyheadoffset[LO,RE]{4.5cm}
\fancyfootoffset[LO,RE]{4.5cm}


\begin{document}
\thispagestyle{empty} % this page has no header  
\setlength{\parindent}{0cm}
{\large \bf A. Rajesh Prashanth (DoB: November 03, 1994)}
\begin{resume}





%+---------------------------------------------------------
%+Contact 
%+---------------------------------------------------------

\begin{flushright}
\bf {251-A, 8\textsuperscript{th} Cross Road, Prakash Nagar,\\
Thiruninravur, Chennai-602 024, India.\\
%50, K K Road, Venkatapuram,\\
%Ambattur, Chennai-600 053, India.\\
Tel: +91 44 65160618, +91 81908 05640.\\ 
Email: \href{mailto:rajeshprasanth@rediffmail.com}{rajeshprasanth@rediffmail.com}\\
Web: \url{https://sites.google.com/site/arajeshprasanth}}\\
\end{flushright}

%+---------------------------------------------------------
%  Objective
%+---------------------------------------------------------

\section{OBJECTIVE}
To serve the society through the knowledge and skills acquired during under \\graduate education in Electrical and Electronics Engineering.

%+---------------------------------------------------------
%+  Education
%+---------------------------------------------------------

\section{EDUCATION} 
{\sl B.E., Electrical and Electronics Engineering,} \hfill (2016) \\
                Prathyusha Engineering College, Chennai-602 025.
					\\(formerly Prathyusha Institute of Technology and Management)
					\\CGPA: 8.24/10.

{\sl Higher Secondary Education,} \hfill (2012)\\
                Jaya Matriculation Higher Secondary School, Thiruninravur, Chennai-602 024.\\ 
                Percentage marks: 84.67 \%

{\sl Secondary Education,} \hfill (2010)\\
                Jaya Matriculation Higher Secondary School, Thiruninravur, Chennai-602 024.
 

%+---------------------------------------------------------
%+  Area of interest
%+---------------------------------------------------------

\section{AREA OF INTEREST}
Instrumentations, Solar radiation measurements, Organic photovoltaics,\\ Computational Material Science, Quantum simulations, Scientific software \\development.

%+---------------------------------------------------------
%+  Computer skills
%+---------------------------------------------------------

\section{COMPUTER SKILLS}
{\sl Operating Systems:} Linux(Fedora, Ubuntu, CentOS), Windows(upto 8.1).\\
{\sl Languages \& Packages:} FORTRAN, C, C++, Python, Bash scripting, \\\LaTeX, Matlab, Pspice.\\
{\sl Codes for Material simulation:} Quantum Espresso, SIESTA, BerkeleyGW,\\ USPEX, XCrySDen.

%+---------------------------------------------------------
%+  Software development
%+---------------------------------------------------------

\section{SOFTWARE DEVELOPMENT}
Chief developer for  \textgravedbl XtalCalculator\textacutedbl --- A code for computing physical parameters in crystals. The source code can be downloaded under GNU/GPL at the project page \url{http://sourceforge.net/projects/xtalcalculator/}

%+---------------------------------------------------------
%+  literary languages
%+---------------------------------------------------------

\section{LITERARY LANGUAGES} 
Fluent in reading, writing and speaking in English and Tamil.\\

%+---------------------------------------------------------
%+  Trainings
%+---------------------------------------------------------

\section{TRAININGS }
A week long inplant training at M/s Lucas Indian Services,\hfill (Jun 16-21, 2014) \newline Ambattur Industrial Estate, Chennai-58. 

%+---------------------------------------------------------
%+  Certification
%+---------------------------------------------------------

\section{CERTIFICATIONS}\vspace*{-0.48 cm}
\begin{enumerate}
    \item	{Certification on \textgravedbl Introduction to Linux.\textacutedbl }\hfill{Jul 2015}\\
Offered by edX with the support of The Linux Foundation, San Francisco, United States of America. 
	 \item {IBM-CE Software Foundation (Advanced) course. \hfill {Jul 2013-Jan 2014}}
\newline Offered by IBM Career Education program.
\end{enumerate}

%+---------------------------------------------------------
%+  Projects
%+---------------------------------------------------------

\section{PROJECTS}\vspace*{-0.48 cm} %28
\begin{enumerate}
\item {\sl \textquotedblleft A Novel design and Characterization of Pyranometer for Precision Solar Radiation Measurements\textquotedblright, End-course project, Funded by Prathyusha Institute of Technology and Management, Chennai, Jan-Feb, 2016.}
\item {\sl \textquotedblleft Installation of solar powered street lamps for public utility at Paparampakkam village (20 W, 12 Hrs, Open air model).\textquotedblright, Funded by Prathyusha Institute of Technology and Management, Chennai, Feb-Mar, 2015.}
\item {\sl \textquotedblleft Installation of solar powered pollution free garden lamps (20W, 8 Hrs, Open air model).\textquotedblright, Funded by Prathyusha Institute of Technology and Management, Chennai, Nov-Dec, 2014.}
\item {\sl \textquotedblleft Design and Installation of solar powered street lamps (20W, 8 Hrs, Open air model).\textquotedblright , Funded by Prathyusha Institute of Technology and Management, Chennai, Jul-Aug, 2014.}
\end{enumerate} 


%+---------------------------------------------------------
%+  Project contest
%+---------------------------------------------------------
\section{PROJECT CONTESTS}\vspace*{-0.48 cm} %28
\begin{enumerate}
\item {\sl Participation at \textquotedblleft Engineer Infinite 2016\textquotedblright, as a part of ELECRAMA 2016} 
\\Organized by Indian Electrical and Electronic Manufacturer's Association (IEEMA), Bangaluru on Jan 13-17, 2016.
\item {\sl Participation as exhibitor at \textquotedblleft Open House and Project contest\textquotedblright}
\\Organized by Dhanalakshmi College of Engineering, Tambaram, Chennai on Sept 3-5, 2015.
\end{enumerate}

%+---------------------------------------------------------
%+  workshops
%+---------------------------------------------------------

\section{WORKSHOPS}\vspace*{-0.48 cm}
\begin{enumerate}
\item {\sl One Day workshop on Embedded systems.}
\\Organized by Tamil Nadu Science and Technology Centre, \\Chennai on May 6, 2015.
\item {\sl India's first cloud computing championship.} 
\\Organized by IFC3-India, IIT-Bhuvaneswar and Prathyusha Institute of Technology and Management, Chennai on Feb 21 and 22, 2015. 
\item {\sl 8\textsuperscript{th} USPEX workshop on Crystal Structure Prediction.} 
\\Organized by Stony Brook University, USA, International Union of \\Crystallography, IUCr-London and Shiv Nadar University, Noida, India, Jan 20-24, 2015.
\end{enumerate}        

%+---------------------------------------------------------
%+  Honors and awards
%+---------------------------------------------------------

\section{HONORS AND AWARDS}\vspace*{-0.48 cm}
\begin{itemize}
    \item Best Project Design award for the End course project \textquotedblleft A Novel design and Characterization of Pyranometer for Precision Solar Radiation Measurements\textquotedblright, April, 2016.
    \item Appreciation from the college for the project \textquotedblleft Design and Installation of solar powered street lamp.\textquotedblright
\end{itemize}

%+---------------------------------------------------------
%+  Community services
%+---------------------------------------------------------

\section{COMMUNITY SERVICES} \vspace*{-0.48 cm}
\begin{itemize}
    \item Invitee for talk on the solar powered appliances in a village through \\ community service under National Service Scheme - Feb 2015.       
\item Active member in polio drop administration camp in collaboration with the Department of Public Health  Services (Government of Tamil nadu), Chennai, Tamil Nadu.
\end{itemize} 

%+---------------------------------------------------------
%+  Others
%+---------------------------------------------------------

\section{OTHERS}
Electronic hobbyist, Domestic appliances maintainance.

%+---------------------------------------------------------
%+  Reference
%+---------------------------------------------------------

%\section{REFERENCE}\vspace*{-0.28 cm}
%\begin{enumerate}
%    \item Ex.Capt. R. G. Thayakaran,\\
%			 Director, Placements and trainings,\\
%			 Prathyusha Institute of Technology and Management,\\
%			 Thiruvallur, Chennai-602 025.\\
%			 Phone: 91 9566106682.
%	 \item Mr.S. Krishna Kumar,\\
%			 Head , 
%          Department of Electrical and Electronics Engineering,\\ 
%          Prathyusha Institute of Technology and Management,\\
%			 Thiruvallur, Chennai-602 025.\\
%          Phone: 91 9840789302
%			 
%\end{enumerate}
\end{resume}
\end{document}
